Revisiting 'Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation

### 2023-07-04 analysis/article/paper.qmd
repair table lables & some writing

keywords: 
  - Public goods
  - Dynamic games
  - Reproducibility
  - Generalizability
  - Online Experiment
  - Climate change mitigation
date: last-modified
bibliography:  ../biblio.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal of Behavioral and Experimental Economics
      formatting: review
      model: 3p
      layout: onecolumn
      cite-style: authoryear
---

@@

Today's actions are tomorrow's result. There are many settings in which current decisions affect future outcomes and with it, future decision spaces. 
<!-- Think of lifetime consumption‐smoothing and save more tomorrow -->
Opting for environmentally friendly policies today not only reduces carbon dioxide emissions immediately but also helps us to reach the Paris climate targets tomorrow. Deferring these policies, may not necessarily prevent us from reaching these targets, but it requires more effort in the future compared to a path that includes immediate action [@HaenselEtAl2022]. Aiming at certain goals, today's actions (or the omission thereof) not only affect intermediate outcomes but also the number of paths one can choose from that lead to that specific goal.

Public good (or public bad) games---although often intended to inform climate policies [e.g. @MilinskiEtAl2006; @TavoniEtAl2011; @Hauser2014; @BrickEtAl2015; @GomezEtAl2018; @CalzolariEtAl2018; @CookEtAl2019]---miss these temporal interdependencies simply because participants have the same set of actions in each period. Accordingly, participants' actions in a given period do not affect their action space in subsequent periods. To see the lack of realism, consider carbon dioxide emissions, where the current stock will last for well over a millennium [@Inman2008; @CalzolariEtAl2018]. Playing with fresh endowments in each period is as if one could just undo carbon dioxide emissions at no cost.

A game designed by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017 hereafter, GMTV] as well as Stefan Große (unpublished), shows that it is fairly simple to add this element of realism. They incorporate interdependencies into a _dynamic_ public goods game (dPGG) by defining endowments as the income of previous periods. Consequently, participants' actions in a given period affect their number of actions in subsequent periods: the more (less) they earn now, the more (less) they can contribute in the next period. Importantly, this modification qualitatively yields the same rational predictions as the static game (i.e. free-riding and the under-provision of the public good). It is thus, equally well suited to study dilemma situations.

Because there is surprisingly little experimental research on interdependencies^[See e.g. @BattagliniEtAl2016, @Rockenbach2017 or @Moser2019.], I reproduced one of GMTVs' treatments to compare dynamics across (in)experienced samples to investigate its generalizability.
@GKLS2020 find that static public goods games do not generalize well to real-world climate action. They also find that generalizability depends on the structural resemblance of the public goods game with the context of climate change mitigation: Greater resemblance improves generalizability. Because GMTVs' dynamic setting has a more realistic property—namely, interdependencies—one would expect it to be better suited to inform public policy. To test this intuition, I not only ran the experiment with different samples but also
<!--, that is, with participants who make their decisions in an environment which is more natural than the lab.-->
observed the participants' behavior in voluntary climate actions (VCA).^[The VCA is a (charitable) dictator game where each participant is a dictator dividing her budget between herself and some organization linked to the reduction of CO2 emissions. @EckelGrossman1996 were the first to implement a charitable dictator game observing contributions of 30% of the endowments. Like @GKLS2020, @CarpenterEtAl2008 report that students make lower contributions to charity than community members.] This yielded a setting similar to the one of @GKLS2020, which allows me to analyze how behavior in the abstract game translates into real-world action across samples. This research shows that the dynamic setting _does not_ add any advances to the generalizability of results.

@AGM2018 conducted static public goods games in the lab and on MTurk to draw (and report) lessons from online experimentation. This study extends this literature [see, e.g., @KrantzEtAl1997, @AmirEtAl2012; @KleinEtAl2014; @PaolacciChandler2014; @GoodmanPaolacci2017; @SnowbergYariv_2021; @GuptaRigottiWilson_2021; @BusoEtAl2021] by focusing on an _inconvenient_ sample (i.e. one that is a completely inexperienced sample [see also @BenndorfEtAl2017] that has not been exposed to interactive experiments before) playing a computationally more complex game during a time that was characterized by more inattentiveness in online samples [@ArecharRand2021; @PeytonEtAl2022]. This required me to design robust (and thus, more complex) software to minimize attrition. I collected para data [@Parsons2022 p. 12]---which capture screen time and survey navigation, for instance---to assess the desired fluency and feasibility of the experiment. Like @AGM2018, this research is of practical relevance as it reports on the robust design that made the dynamic game feasible.

@@

Now, 20 years later, we accustom ourselves to mechanisms designed to unravel the fuzzy back-and-forth between exploratory and confirmatory research. Prominently, pre-registrations and pre-analysis plans (PAP) [see, e.g., @BrodeurEtAl2022] were established to tie the researchers' hands with respect to p-hacking and ex-post theorizing when doing confirmatory research---reducing observable discrepancies between Daryl Bem's above-mentioned (a) and (b).

While pre-registrations and PAPs could help to make empirical sciences more credible, they come at costs that are discussed by @Olken2015, @PageEtAl2021, as well as @Krishna2021, @SimmonsEtAl2021, and @PhamEtAl2021. One important concern is that strict pre-registrations may severely discount any additional analysis of the data inspired by surprise results. In practice, there are at least two ways to approach that problem: First, one could (and should) add unforeseen analyses to the article but label them as exploratory. Second, one could write a minimal pre-registration leaving enough degrees of freedom for the researcher to incorporate such surprises without further notice. The key difference between the two approaches is the deliberate omission of transparency.

For the field of neuropsychopharmacology @WaldronAllen2022 document that the depth of pre-registrations differs indeed: it is spanning from notes on hypotheses only to fully specified, detailed experimental protocols with accompanying power analyses and sampling plans. Treating all pre-registrations equally may thus lead to an adverse effect: If one can acquire the _'pre-registered'_ label with minimal effort and maximum flexibility, the label itself may run into danger to become worthless and to miss the target of making science more credible.

This erosion of credibility can be avoided by the means of transparency---not because transparency can tighten the ties but because it facilitates scrutiny, policing [see @AnkelPetersFialaNeubauer2023] and forensics [see, e.g., @SimonsohnEtAl2023]: transparent research practices make it easier for others to track and understand a researcher's reaction to surprises in the data, which, in turn, gives the researcher more flexibility to react to these surprises. As additional transparency is associated with additional effort, I propose version control as a natural and easy-to-implement solution augmenting pre-registrations.

Contemporary experimental research is, to a certain degree, a computational science: experiments often require complex software and the analysis thereof can result in complicated scripts. In addition, much research is carried out in collaborative efforts. For these reasons alone, it makes sense to implement version control systems such as GitHub and GitLab as well as OSF (albeit less powerful) that ensure that files are stored consistently and that changes are tracked. When these systems are implemented in the whole research process, one can archive different states of the software and visualize differences between different states. For instance, one can archive the analysis before and after the data was collected or the experimental software used in a pilot and the eventual experiment. Importantly, one can keep projects private and change their visibility to public only after the corresponding article is accepted for publication. Taken together, these features _automatically_ enhance transparency and facilitate scrutiny, policing, and forensics whilst also making software development and collaboration more efficient. As a consequence, the implementation and eventual disclosure of version control come not only with meta-scientific but also with organizational benefits.

The experiment reported in this article qualifies for the _'pre-registered'_ label at first glance:
The analysis was pre-registered in the American Economic Association's RCT Registry [@preregistration]. Further, I pre-registered the exact analyses I planned to run (PAP) when I designed the experiment on [GitHub](https://github.com/Howquez/GMTV/tree/July21Replication/analysis/R).^[bit.ly/3Pnak5H. To run the code, you need to execute the .Rmd files in this repository in the order that is indicated by file names. Detailed instructions can be found in the README file accompanying the analysis scripts.]

At second glance, the analysis that made the most sense after having collected the data and that is reported here is a little different though: Because the more representative subject pool was exhausted earlier than expected, I recruited students which opened up a new research direction: assessing generalizability. Hence, this article combines both confirmatory as well as exploratory research.

Accordingly, I edited many of the analysis scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/GMTV/blob/main/analysis/article/paper.qmd): https://bit.ly/43LCyLw] However, because the originally planned analysis code is archived and reproducible, these changes are transparent. Importantly, I followed a literate programming approach [@Knuth_1984; @AkhtarYe_2023]. Hence, all documents needed to analyze the data and to write the report stem from the same source. This establishes consistence between the commands one tells the statistical software to do and the explanation one tells human beings one told the statistical software to do. As such, (a), (b), and the transition from (a) to (b) are not only transparent but also comprehensible.

@@

In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific_ reproduction^[In fact, @Hamermesh2007 uses the term _replication_ instead of _reproduction_. The reason I deviate is that I do not compare different treatments with each other to _replicate_ a treatment effect. Instead, I _reproduce_ the results of one specific treatment arm.] of one treatment of GMTVs' dynamic public goods game. The pure reproduction re-analyzes the original data. [Appendix A](#A:-Pure-Replication) documents [the errors I identified]() in the original paper. The scientific reproduction, where I utilize a different sample drawn from a different population in a different situation, is described in the following sections.

@@

Like GMTV I employ a real giving task after the abstract game. Specifically, I employed a (charitable) dictator game where each participant is a dictator dividing her budget between herself and some organization. Whereas GMTV chose _Doctors without Borders_ as a receiver, I chose another organization in another context: like @GKLS2020, I employed a VCA, where participants could donate any amount of their earnings to offset carbon dioxide (that is, retire emission permits from the EU ETS).^[Importantly, @GKLS2020 made the VCA decision with a fresh endowment _before_ they played the abstract game. I deviate from their procedure to match GMTVs' procedure.]
To ensure that each participant had the same basic level of information about the impact of their decision, I provided some basic information about the mechanism. The information also highlighted that the mitigation came into operation on a European level.
Finally, I informed the participants that the documentation of individual and aggregate contributions was to be posted immediately after the conclusion of the sessions online. To avoid privacy or social image concerns, participants learned their unique and random IDs, which they needed to identify their individual contributions.
The document certified that their contributions have been used to offset [1.82 tons](https://www.compensators.org/compensatelist/?searchterm=stefan+traub) of carbon dioxide emissions.

@@

Throughout this paper, I will compare the results of my experiment with the results of GMTVs' NOPUNISH 10 Period treatments. I am thus, referring to three different samples utilized at two points in time: the University of Nottingham's students (in late 2012), Hamburg's citizens, and the University of Hamburg's students (both in July 2021). @tbl-sample-properties gives an overview.

@@

I chose oTree [@oTree] to implement the experiment because it is open-source, well-documented, and very flexible. Its [Bootstrap](https://getbootstrap.com/) (a powerful frontend toolkit) integration allowed me to make the graphical user interface interactive, appealing, and easy to navigate. The [Highcharts library](https://www.highcharts.com/) made it easy to visualize results and communicate dynamics. Insofar, oTree served as a good tool to enhance the participants' user experience and thus, to make dropouts less likely.

Which features were required to handle dropouts? First, participants had to be matched to form a group _after_ comprehension questions were answered successfully. Importantly, participants were grouped by the order they answered these questions to reduce waiting times. While waiting for other players to form the group, the participants saw a wait-page informing them that they are waiting for other participants to arrive and that they do not have to wait for longer than 10 minutes. The screen also informed them that they would receive a _patience bonus_ of one Euro after the expiration of that time (or what was left of it). Second, participants only had 10 minutes to make the first contribution and 4 minutes for the remaining contributions. After this time expired, participants were replaced by bots that made random contributions. In this case, the remaining group members were informed about the replacement. Both features were implemented to limit wait times and boredom for other participants. @sec-feasibility shows that the first feature became effective in some cases, whereas the second feature did not.

@@

While I stuck to GMTVs' protocol as close as possible, I deviated in a few aspects. First, the instructions were German and also covered topics inherent to the online setting (dropouts and bots, for instance). Second, I used another software (oTree instead of zTree) which also affected the graphical user interface participants were exposed to. Third, GMTV gave participants the opportunity to donate to _Doctors without Borders_ whereas I offered carbon dioxide offsets.

@@

The experiment lasted around `r total_completion_time` minutes on average. The earnings  averaged `r earningsMean %>% round(digits = 2)` Euros (sd = `r earningsSD  %>% round(digits = 2)`).^[This value include earnings from the incentivized risk elicitation task that is not part of the analysis.]

@@

In particular, do the two samples' contributions follow the same path over the 10 periods they played? The answer is _yes and no_. @fig-share-of-contributions and @tbl-contribution-periods illustrate that the samples make similar contributions at the beginning and the end of the game but behave differently in between. More precisely, the left panel--depicting the average contributions in absolute terms--shows that the original sample contributed more than the reproduction sample _in all but the first and last period_.^[In period five, this difference is significant: a two-sided rank sum test yields p=`r rs2`. ] For this reason, the original sample's behavior differs from the reproduction sample's behavior in two aspects: it contributes more and exhibits a considerable drop in the last period (whereas the reproduction sample's contributions flatten).

Note that increasing contributions over time imply increasing endowments over time. Hence, absolute contributions do not tell much about the willingness to cooperate. For this reason, the right panel in @fig-share-of-contributions shows the average _share of endowments contributed_ over time. Both samples exhibit a similar pattern: their share of endowments contributed declined and did not stabilize. However, both samples also differ with respect to one aspect: the reproduction sample's share of contributions declines faster. This is mirrored by a two-sided rank sum test which is only significant at a five percent level in periods three and four.

@@

This is remarkable given the different sample and language, the different software and user interface as well as the online setting during the COVID-19 pandemic. The result suggests that by and large, the sum of these factors did not affect people’s preferences towards cooperation.

@@

I first comment on the selection into the experiment: It was difficult to recruit the sample. The panel counted 1.209 non-students of which I was able to recruit `r main[student == FALSE, .N]` participants who finished the experiment---even though I varied the weekdays and timing of the sessions (which were conducted during a nationwide lockdown with home office regime). For this reason, I also recruited students in the last session which explains the relatively large number of showups in @tbl-meta. Although I intended to refrain from the recruitment of students initially, this particular sub-sample enabled me to investigate the generalizability of my results as I will discuss in  @sec-generalizability.

@@

Considering attrition, I find that it did not affect the interactive experiment at all. To elaborate, I differentiate between dropouts and residuals:  Participants who could not be matched to other group members are called residuals. Participants who intentionally left the experiment are called dropouts. Residuals did not participate in the experiment _by design_. Dropouts did not participate in the experiment _by choice_. Out of `r meta[, sum(showups)]` people who showed up, I count `r meta[, sum(residuals)]` residuals and `r meta[, sum(dropouts)]` dropouts. All of the residuals waited to be matched to a group unsuccessfully before they got paid one Euro for their patience. In contrast, all of the dropouts left while reading the instructions and before being matched to other group members. Moreover, they got no payment at all. Hence, attrition was no concern considering the dynamic public goods game or the expenses.

@@

          model.numbers = TRUE,
          dep.var.caption  = "Tobit Regression censoring below 0 and above 100",
          dep.var.labels = "VCA Donation as Share of Earnings",
          header=FALSE,
          intercept.bottom = TRUE,
          order = c(1, 2, 6, 3, 4, 5),
          covariate.labels = c("First-period contribution in percent", "Student (1 = yes)", "First-period contr. x Student", "Age", "Female (1 = yes)", "Risk Aversion (1-12)"),
          type = "latex", digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
          )
```

@@

I gratefully acknowledge support by the German Research Foundation (DFG) under Germany’s Excellence Strategy, cluster EXC 2037 “Climate, Climatic Change, and Society” (project 390683824). I thank Stefan Traub, whoever proofreads this and the participants of the CLICCS B5 group for helpful discussions.

>>>>

keywords: 
  - Public goods
  - Dynamic games
  - Reproducibility
  - Generalizability
  - Online experiment
  - Climate change mitigation
date: last-modified
bibliography:  ../biblio.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal of Behavioral and Experimental Economics
      formatting: review
      model: 3p
      layout: onecolumn
      cite-style: authoryear
---

@@

Today's actions are tomorrow's result. There are many settings in which current decisions affect future outcomes and with it, future decision spaces. 
<!-- Think of lifetime consumption‐smoothing and save more tomorrow -->
For example, opting for environmentally friendly policies today not only reduces carbon dioxide emissions immediately, but also helps us reach the Paris climate targets tomorrow. Deferring these policies to a later state, may not necessarily prevent us from reaching these targets, but it will require more effort in the future compared to a path which includes immediate action [@HaenselEtAl2022]. Aiming at certain goals, today's actions (or the omission thereof) not only affect intermediate outcomes but also the number of viable paths one can choose from that lead to that specific goal.

Public good (or public bad) games---although often intended to inform climate policies [e.g. @MilinskiEtAl2006; @TavoniEtAl2011; @Hauser2014; @BrickEtAl2015; @GomezEtAl2018; @CalzolariEtAl2018; @CookEtAl2019]---fail to include these temporal interdependencies simply because participants have the same set of actions in each period. Accordingly, participants' actions in a given period do not affect their action space in subsequent periods. To better capture the lack of realism, consider carbon dioxide emissions, where the current stock will last for well over a millennium [@Inman2008; @CalzolariEtAl2018]. Playing with fresh endowments in each period is as if one could just undo carbon dioxide emissions at no cost.

A game designed by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017 hereafter, GMTV] as well as Stefan Große (unpublished), shows that it is relatively simple to include this element of realism. They incorporate interdependencies into a _dynamic_ public goods game (dPGG) by defining endowments as the income of previous periods. Consequently, participants' actions in a given period affect their number of actions in subsequent periods: the more (less) they earn now, the more (less) they can contribute in the next period. Importantly, this modification qualitatively yields the same rational predictions as the static game (i.e. free-riding and the under-provision of the public good). It is thus, equally well suited to study dilemma situations.

As there is surprisingly little experimental research on interdependencies^[See e.g. @BattagliniEtAl2016, @Rockenbach2017 or @Moser2019.], I reproduced one of GMTVs' treatments to compare dynamics across (in)experienced samples to investigate its generalizability.
@GKLS2020 find that static public goods games do not generalize well to real-world climate action. They also find that generalizability is dependent on the structural resemblance of the public goods game with the context of climate change mitigation: Greater resemblance improves generalizability. Because GMTVs' dynamic setting has a more realistic property—namely, interdependencies—one would expect it to be better suited to inform public policy. As means to test this intuition, I not only ran the experiment with different samples but also
<!--, that is, with participants who make their decisions in an environment which is more natural than the lab.-->
observed the participants' behavior in voluntary climate actions (VCA).^[The VCA is a (charitable) dictator game where each participant is a dictator dividing her budget between herself and some organization linked to the reduction of CO2 emissions. @EckelGrossman1996 were the first to implement a charitable dictator game observing contributions of 30% of the endowments. Like @GKLS2020, @CarpenterEtAl2008 report that students make lower contributions to charity than community members.] This yielded a setting similar to the one of @GKLS2020, which allows me to analyze how behavior in the abstract game translates into real-world action across samples. This research shows that the dynamic setting _does not_ add any advances to the generalizability of results.

@AGM2018 conducted static public goods games in the lab and on MTurk to draw (and report) lessons from online experimentation. This study extends this literature [see, e.g., @KrantzEtAl1997, @AmirEtAl2012; @KleinEtAl2014; @PaolacciChandler2014; @GoodmanPaolacci2017; @SnowbergYariv_2021; @GuptaRigottiWilson_2021; @BusoEtAl2021] by focusing on an _inconvenient_ sample (i.e. one that is a completely inexperienced sample [see also @BenndorfEtAl2017] that has not been exposed to interactive experiments before) playing a computationally more complex game during a time that was characterized by more inattentiveness in online samples [@ArecharRand2021; @PeytonEtAl2022]. With this background in mind, it required me to design robust (and thus, more complex) software to minimize attrition. I collected para data [@Parsons2022 p. 12]---which capture screen time and survey navigation, for instance---to assess the desired fluency and feasibility of the experiment. Like @AGM2018, this research is of practical relevance as it reports on the robust design that made the dynamic game feasible.

@@

Today, 20 years later, we have accustomed ourselves to mechanisms designed to unravel the fuzzy back-and-forth between exploratory and confirmatory research. Prominently, pre-registrations and pre-analysis plans (PAP) [see, e.g., @BrodeurEtAl2022] were established as a means to tie the researchers' hands with respect to p-hacking and ex-post theorizing when doing confirmatory research---reducing observable discrepancies between Daryl Bem's above-mentioned (a) and (b).

While pre-registrations and PAPs could help to make empirical sciences more credible, they come at costs that are discussed by @Olken2015, @PageEtAl2021, as well as @Krishna2021, @SimmonsEtAl2021, and @PhamEtAl2021. One important concern is that strict pre-registrations may severely discount any additional analysis of the data inspired by surprise results. In practice, there are at least two ways to approach that problem: First, one could (and should) add unforeseen analyses to the article but be sure to label them as exploratory. Second, one could write a minimal pre-registration leaving enough degrees of freedom for the researcher to incorporate such surprises without further notice. The key difference between the two approaches is the deliberate omission of transparency.

For the field of neuropsychopharmacology @WaldronAllen2022 document that the depth of pre-registrations differs indeed: it is spanning from notes on hypotheses only to fully specified, detailed experimental protocols with accompanying power analyses and sampling plans. Treating all pre-registrations equally may thus lead to an adverse effect: If one can acquire the _'pre-registered'_ label with minimal effort and maximum flexibility, the label itself may run into danger by becomming worthless and to missing the target of making science more credible.

This erosion of credibility can be avoided by the means of transparency---not because transparency can tighten the ties but because it facilitates scrutiny, policing [see @AnkelPetersFialaNeubauer2023] and forensics [see, e.g., @SimonsohnEtAl2023]: transparent research practices make it easier for others to track and understand a researcher's reaction to surprises within the data, which, in turn, gives the researcher more flexibility to react to said surprises. As additional transparency is associated with additional effort, I propose version control as a natural and easy-to-implement solution augmenting pre-registrations.

Contemporary experimental research is, to a certain degree, a computational science: experiments often require complex software and the analysis thereof can result in complicated scripts. In addition, much research is carried out in collaborative efforts. For these reasons alone, it makes sense to implement version control systems such as GitHub and GitLab as well as OSF (albeit less powerful) that ensure that files are stored consistently and that changes are tracked. When these systems are implemented throughout the entire research process, one can archive different states of the software and visualize differences between different states. For instance, one can archive the analysis before and after the data was collected or the experimental software used in a pilot and the eventual experiment. Importantly, one can keep projects private and change their visibility to public only after the corresponding article is accepted for publication. Taken together, these features _automatically_ enhance transparency and facilitate scrutiny, policing, and forensics whilst making software development and collaboration more efficient. As a consequence, the implementation and eventual disclosure of version control come not only with meta-scientific but also with organizational benefits.

The experiment reported in this article qualifies for the _'pre-registered'_ label at first glance:
The analysis was pre-registered in the American Economic Association's RCT Registry [@preregistration]. Furthermore, I pre-registered the exact analyses I planned to run (PAP) when I designed the experiment on [GitHub](https://github.com/Howquez/GMTV/tree/July21Replication/analysis/R).^[bit.ly/3Pnak5H. To run the code, you need to execute the .Rmd files in this repository in the order that is indicated by file names. Detailed instructions can be found in the README file accompanying the analysis scripts.]

At second glance, the analysis that made the most sense after having collected the data and that is reported here is a little different though: Because the more representative subject pool was exhausted earlier than anticipated, I recruited students which opened up a new research direction: assessing generalizability. Hence, this article combines both confirmatory as well as exploratory research.

Accordingly, I edited many of the analysis scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/GMTV/blob/main/analysis/article/paper.qmd): https://bit.ly/43LCyLw] However, because the originally planned analysis code is archived and reproducieable, these changes are transparent. Importantly, I followed a literate programming approach [@Knuth_1984; @AkhtarYe_2023]. Hence, all documents needed to analyze the data and to write the report stem from the same source. This establishes consistence between the commands one tells the statistical software to do and the explanation one tells human beings one told the statistical software to do. As such, (a), (b), and the transition from (a) to (b) are not only transparent but also comprehensible.

@@

In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific_ reproduction^[In fact, @Hamermesh2007 uses the term _replication_ instead of _reproduction_. The reason I deviate is that I do not compare different treatments with each other to _replicate_ a treatment effect. Instead, I _reproduce_ the results of one specific treatment arm.] of one treatment of GMTVs' dynamic public goods game. The pure reproduction re-analyzes the original data. [Appendix A](#A:-Pure-Replication) documents [the errors I identified]() within the original paper. The scientific reproduction, where I utilize a different sample drawn from a different population in a different situation, is described in the following sections.

@@

In the same stroke as GMTV I employ a real giving task after the abstract game. Specifically, I employed a (charitable) dictator game where each participant is a dictator dividing her budget between herself and some organization. Whereas GMTV chose _Doctors without Borders_ as a receiver, I chose another organization in another context: like @GKLS2020, I employed a VCA, where participants could donate any amount of their earnings to offset carbon dioxide (that is, retire emission permits from the EU ETS).^[Importantly, @GKLS2020 made the VCA decision with a fresh endowment _before_ they played the abstract game. I deviate from their procedure to match GMTVs' procedure.]
To ensure that each participant had the same basic level of information about the impact of their decision, I provided some basic information about the mechanism. The information also highlighted that the mitigation came into operation on a European level.
Finally, I informed the participants that the documentation of individual and aggregate contributions was to be posted immediately after the conclusion of the sessions online. To avoid privacy or social image concerns, participants learned their unique and random IDs, which they needed to identify their individual contributions.
The document certified that their contributions have been used to offset [1.82 tons](https://www.compensators.org/compensatelist/?searchterm=stefan+traub) of carbon dioxide emissions.

@@

Throughout this paper, I will compare the results of my experiment with the results of GMTVs' NOPUNISH 10 Period treatments. I am thus, referring to three different samples utilized at two different points in time: the University of Nottingham's students (in late 2012), Hamburg's citizens, and the University of Hamburg's students (both in July 2021). @tbl-sample-properties gives an overview.

@@

I chose oTree [@oTree] to implement the experiment because it is open-source, well-documented, and very flexible. Its [Bootstrap](https://getbootstrap.com/) (a powerful frontend toolkit) integration allowed me to make the graphical user interface interactive, appealing, and easy to navigate. The [Highcharts library](https://www.highcharts.com/) additionally made it easy to visualize results and communicate dynamics. Insofar, oTree served as a good tool to enhance the participants' user experience and thus, to make dropouts less likely.

Which features were required to handle dropouts? First, participants had to be matched to form a group _after_ comprehension questions were answered successfully. Importantly, participants were grouped according to the order they answered these questions to reduce waiting times. While waiting for other players to form the group, the participants saw a wait-page informing them that they are waiting for other participants to arrive and that they do not have to wait for longer than 10 minutes. The screen also informed them that they would receive a _patience bonus_ of one Euro after the expiration of that time (or what was left of it). Second, participants only had 10 minutes to make the first contribution and 4 minutes for the remaining contributions. After this time expired, participants were replaced by bots that made random contributions. In this case, the remaining group members were informed about the replacement. Both features were implemented to limit wait times and boredom for other participants. @sec-feasibility shows that the first feature became effective in some cases, whereas the second feature did not.

@@

Overall, I stuck to GMTVs' protocol as close as possible, however, I deviated in a few aspects. First, the instructions were German and also covered topics inherent to the online setting (dropouts and bots, for instance). Second, I used another software (oTree instead of zTree) which also affected the graphical user interface participants were exposed to. Third, GMTV gave participants the opportunity to donate to _Doctors without Borders_ whereas I offered carbon dioxide offsets.

@@

The experiment lasted on average for around `r total_completion_time` minutes. The earnings  averaged `r earningsMean %>% round(digits = 2)` Euros (sd = `r earningsSD  %>% round(digits = 2)`).^[This value include earnings from the incentivized risk elicitation task that is not part of the analysis.]

@@

In particular, do the two samples' contributions follow the same path over the 10 periods they played? The answer is both _yes and no_. @fig-share-of-contributions and @tbl-contribution-periods illustrate that the samples make similar contributions at the beginning and the end of the game but behave differently in between. More precisely, the left panel--depicting the average contributions in absolute terms--shows that the original sample contributed more than the reproduction sample _in all but the first and last period_.^[In period five, this difference is significant: a two-sided rank sum test yields p=`r rs2`. ] For this reason, the original sample's behavior differs from the reproduction sample's behavior in two aspects: it contributes more and exhibits a considerable drop in the last period (whereas the reproduction sample's contributions flatten).

Note that increasing contributions over time imply increasing endowments over time. Hence, absolute contributions do not say much about the willingness to cooperate. For this reason, the right panel in @fig-share-of-contributions shows the average _share of endowments contributed_ over time. Both samples exhibit a similar pattern: Their share of endowments contributed declined and did not stabilize. However, both samples also differ with respect to one aspect: the reproduction sample's share of contributions declines faster. This is mirrored by a two-sided rank sum test which is only significant at a five percent level in periods three and four.

@@

This finding is remarkable given the different sample and language, the different software and user interface as well as the online setting during the COVID-19 pandemic. The result suggests that by and large, the sum of these factors did not affect people’s preferences towards cooperation.

@@

I first comment on the selection into the experiment: It was difficult to recruit the sample. The panel counted 1.209 non-students of which I was able to recruit `r main[student == FALSE, .N]` participants who finished the experiment---even though I varied the weekdays and timing of the sessions (which were conducted during a nationwide lockdown under mandatory home office regime). For this reason, I also recruited students in the last session which explains the relatively large number of showups in @tbl-meta. Although I intended to refrain from the recruitment of students initially, this particular sub-sample enabled me to investigate the generalizability of my results as I will discuss in  @sec-generalizability.

@@

Considering attrition, I find that it did not affect the interactive experiment at all. To elaborate, I differentiate between dropouts and residuals:  Participants who could not be matched to other group members are called residuals. Participants who intentionally left the experiment are called dropouts. Residuals did not participate in the experiment _by design_. Dropouts did not participate in the experiment _by choice_. Out of `r meta[, sum(showups)]` people who showed up, I count `r meta[, sum(residuals)]` residuals and `r meta[, sum(dropouts)]` dropouts. All of the residuals waited to be matched to a group unsuccessfully before they got paid one Euro for their patience. In contrast, all of the dropouts left while reading the instructions and before being matched to other group members. Moreover, they received no payment at all. Hence, attrition was no concern considering the dynamic public goods game or the expenses.

@@

          model.numbers = TRUE,
          dep.var.caption  = "Tobit Regression censoring below 0 and above 100",
          dep.var.labels = "VCA Donation as Share of Earnings",
          header=FALSE,
          intercept.bottom = TRUE,
          order = c(1, 2, 5, 3, 4),
          covariate.labels = c("First-period contribution in percent", "Student (1 = yes)", "First-period contr. x Student", "Age", "Female (1 = yes)", "Risk Aversion (1-12)"),
          type = "latex", digits = 2, omit.stat = c("adj.rsq", "f"), df = FALSE
          )
```

@@

I gratefully acknowledge support by the German Research Foundation (DFG) under Germany’s Excellence Strategy, cluster EXC 2037 “Climate, Climatic Change, and Society” (project 390683824). I thank Stefan Traub, Alexandrea Swanson, and the participants of the CLICCS B5 group for helpful discussions.
